When, why, and how to avoid, prefer, or tolerate inbreeding

### 2018-03-03 presentation/inbreeding.Rmd
More slides, start on results

<div align="left" style="line-height: 0.6em;">
<span style="font-size: 14px;">
Szulkin M, et al. (2013) *Trends Ecol. Evol.* [**28**:205–211](https://doi.org/10.1016/j.tree.2012.10.016).
</span></div>

@@

<div align="left" style="line-height: 0.6em;">
<span style="font-size: 14px;">
Szulkin M, et al. (2013) *Trends Ecol. Evol.* [**28**:205–211](https://doi.org/10.1016/j.tree.2012.10.016).
</span></div>

@@

<div align="left" style="line-height: 0.6em;">
<span style="font-size: 14px;">
Szulkin M, et al. (2013) *Trends Ecol. Evol.* [**28**:205–211](https://doi.org/10.1016/j.tree.2012.10.016).
</span></div>

@@

<div align="left" style="line-height: 0.6em;">
<span style="font-size: 14px;">
Parker (1979) *Sexual selection and reproductive competition in insects* (pp. 123–166). Parker (2006) *Philos. Trans. Royal Soc. B.* [**361**:235-259](https://doi.org/10.1098/rstb.2005.1785).
</span></div>

@@

<center>
![](images/fem_choice_3.png)
</center>

<div align="left" style="line-height: 0.6em;">
<span style="font-size: 14px;">
Parker (1979) *Sexual selection and reproductive competition in insects* (pp. 123–166). Parker (2006) *Philos. Trans. Royal Soc. B.* [**361**:235-259](https://doi.org/10.1098/rstb.2005.1785).
</span></div>

<center>
![](images/fem_choice_4.png)
</center>

<div align="left" style="line-height: 0.6em;">
<span style="font-size: 14px;">
Parker (1979) *Sexual selection and reproductive competition in insects* (pp. 123–166). Parker (2006) *Philos. Trans. Royal Soc. B.* [**361**:235-259](https://doi.org/10.1098/rstb.2005.1785).
</span></div>

<center>
![](images/fem_choice_5.png)

</center>

<div align="left" style="line-height: 0.6em;">
<span style="font-size: 14px;">
Parker (1979) *Sexual selection and reproductive competition in insects* (pp. 123–166). Parker (2006) *Philos. Trans. Royal Soc. B.* [**361**:235-259](https://doi.org/10.1098/rstb.2005.1785).
</span></div>

@@

</center>
<div align="left" style="line-height: 0.6em;">
<span style="font-size: 14px;">
Parker (1979) *Sexual selection and reproductive competition in insects* (pp. 123–166). Parker (2006) *Philos. Trans. Royal Soc. B.* [**361**:235-259](https://doi.org/10.1098/rstb.2005.1785).
</span></div>

@@

- Account for complex genetic architecture undelrying phenotypes

@@

- **When should we predict selection for a mutant allele causing pre-copulatory inbreeding avoidance or inbreeding preference? [1]**

@@

>>>>

![](images/terms_ia.png)

<div align="left" style="line-height: 0.6em;">
<span style="font-size: 14px;"><br>
Szulkin M, et al. (2013) *Trends Ecol. Evol.* [**28**:205–211](https://doi.org/10.1016/j.tree.2012.10.016). 
Images: [A. C. Duthie](catherineduthiearts@gmail.com)
</span></div>

@@

![](images/terms_ip.png)

<div align="left" style="line-height: 0.6em;">
<span style="font-size: 14px;"><br>
Szulkin M, et al. (2013) *Trends Ecol. Evol.* [**28**:205–211](https://doi.org/10.1016/j.tree.2012.10.016).
Images: [A. C. Duthie](catherineduthiearts@gmail.com)
</span></div>

@@

![](images/terms_it.png)

<div align="left" style="line-height: 0.6em;">
<span style="font-size: 14px;"><br>
Szulkin M, et al. (2013) *Trends Ecol. Evol.* [**28**:205–211](https://doi.org/10.1016/j.tree.2012.10.016).
Images: [A. C. Duthie](catherineduthiearts@gmail.com)
</span></div>

@@

<div align="left" style="line-height: 0.6em;">
<span style="font-size: 14px;"><br>
Parker (1979) *Sexual selection and reproductive competition in insects* (pp. 123–166). Parker (2006) *Philos. Trans. Royal Soc. B.* [**361**:235-259](https://doi.org/10.1098/rstb.2005.1785).
</span></div>

@@

<center>
![](images/fem_choice_3.png)

</center>
<div align="left" style="line-height: 0.6em;">
<span style="font-size: 14px;"><br>
Parker (1979) *Sexual selection and reproductive competition in insects* (pp. 123–166). Parker (2006) *Philos. Trans. Royal Soc. B.* [**361**:235-259](https://doi.org/10.1098/rstb.2005.1785).
</span></div>

@@

</center>
<div align="left" style="line-height: 0.6em;">
<span style="font-size: 14px;"><br>
Parker (1979) *Sexual selection and reproductive competition in insects* (pp. 123–166). Parker (2006) *Philos. Trans. Royal Soc. B.* [**361**:235-259](https://doi.org/10.1098/rstb.2005.1785).
</span></div>

@@

- Account for complex genetic architecture underlying phenotypes

@@

- **When should we predict selection for a alleles causing pre-copulatory inbreeding avoidance or inbreeding preference? [1]**

@@

## Mutant allele underlying inbreeding avoidance

![](images/avoid_over_time.png)

- Fact one of simulation
- Fact two

</div>
<span style="font-size: 18px;">
1. Duthie, AB & JM Reid (2016) *Am. Nat.* [**188**:651-667](https://bradduthie.github.io/Duthie_Reid2016_AppendixB.pdf). From [Appendix B](https://bradduthie.github.io/Duthie_Reid2016_AppendixB.pdf)
</span>

## What to do

Histograms -- females and males, versus neutral, add costs.

Emphasis on stochasticity

Population size important

Selection coefficients, inbreeding coefficients, and delta on a half-sib or cousin

Agreement with an infinite alleles model with 10 loci.
